---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$$regch_1 = \beta treatment_1 + \beta poverty_n + \beta treatment + \beta poverty_n + \beta_0$$

* Describe the population for which you are creating the model.

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.

```{r}

week9_model <- stan_glm(data = week_9,
         reg_chg ~ treatment + poverty_n + poverty_n*treatment,
         refresh = 0) %>%
print(digits = 5)

```

Interpret coefficients:





## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?
Due to the fact that we are not considering 4 years of difference, we may not be
able to answer this question with great precision.
* Describe the ideal Preceptor Table.
In an ideal Preceptor Table, we would be able to see the values for each data
point, including both treatment and control. 
* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

```{r}

station2020 <- tibble(treatment = "local",
                      poverty_n = -1.60835093)

histogram_station <- posterior_predict(week9_model, newdata = station2020) %>%
  as_tibble()

histogram_station %>%
  ggplot(aes(x = `1`)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100, 
                 alpha = .5,
                 position = "identity") + 
  labs(title = "Posterior Distribution for Registration Change in 007/001",
       x = "Registration Change", y = "Probability")

sum(histogram_station$`1` > 0.04) / length(histogram_station$`1`)

```


* Answer the President's question.




## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 


```{r}

week9_model %>%
  as_tibble() %>%
  mutate(local_sigma = treatmentlocal + 2*sigma)

```

